Technical Report

### 2018-06-19 fully-abstract-comp/technical-report.tex
Corollary about pure worlds
Updated safety->reasonable lemma to require pure compatible worlds
typo

@@

\begin{lemma}
  If
  \begin{itemize}
  \item $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\npair{(w,\_)} \in \lrv(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $W_w \oplus W_M$ is defined
  \item $\pwheap[W_w](r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$,
  $w$ is reasonable up to $n$ steps in memory $\Phi.\mem$.
\end{lemma}
\begin{proof}
  Induction over $n$.
  For $n=0$ all words are reasonable.
  For $n>0$, we need to prove four implications:
  \begin{itemize}
  \item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$:

@@

\begin{lemma}
  If
  \begin{itemize}
  \item $\npair{(\reg_S,\_)} \in \lrr(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $W_w \oplus W_M$ is defined
  \item $\pwheap[W_w](r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$,
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$for all $r \not\in \{\pcreg\}$
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
  \end{itemize}
\end{lemma}
\begin{proof}
  We prove the three results separately:
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ for all $r \not\in \{\pcreg\}$:

>>>>

\begin{lemma}
  \label{lem:comp-world-pure-comp-world}
  If $W_1 \oplus W_2$ is defined, then $\purePart{W_1} \oplus \purePart{W_2}$ is defined
\end{lemma}
\begin{proof}
  Follows from Lemma~\ref{lem:purePart-oplus}.
\end{proof}

@@

\begin{lemma}
  If
  \begin{itemize}
  \item $\gc = (\ta,\stkb,\gsigrets,\gsigcloss)$
  \item $\npair{(w,\_)} \in \lrv(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \item $\pwheap[W_w](r_\code) \nequal \codereg{\sigrets,\sigcloss,\code,\gc}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$, $w$ is reasonable up to $n$ steps in memory $\ms_S$ and free stack $\ms_\stk$.
\end{lemma}
\begin{proof}
  Induction over $n$.
  For $n=0$ all words are reasonable.
  For $n>0$, we need to prove four implications:
  \begin{itemize}
  \item If $w = \seal{\sigma_\baddr,\sigma_\eaddr,\_}$, then $[\sigma_\baddr,\sigma_\eaddr] \mathrel{\#} (\gsigrets \cup \gsigcloss)$:

@@

\begin{lemma}
  If
  \begin{itemize}
  \item $\npair{(\reg_S,\_)} \in \lrr(W_w)$
  \item $\memSat{\ms_S,\stk,\ms_\stk,\_}{W_M}$
  \item $\purePart{W_w} \oplus \purePart{W_M}$ is defined
  \item $\pwheap[W_w](r) \nequal \codereg{\sigrets,\sigcloss,\code,(\ta,\stkb)}$
  \item $\dom(\code) \subseteq \ta$
  \item $\sigrets \subseteq \gsigrets$ and $\sigcloss \subseteq \gsigcloss$
  \end{itemize}
  then, with respect to $\code,\ta,\gsigrets,\gsigcloss$,
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ and free stack $\Phi.\ms_\stk$for all $r \not\in \{\pcreg\}$
  \item $\Phi.\mem$, $\Phi.\ms_\stk$ and $\Phi.\stk$ are all disjoint
  \end{itemize}
\end{lemma}
\begin{proof}
  We prove the three results separately:
  \begin{itemize}
  \item $\Phi.\reg(r)$ is reasonable up to $n$ steps in memory $\Phi.\mem$ for all $r \not\in \{\pcreg\}$:
